### 2015-04-10 src/5_2_Proposal.tex
Agregar análisis de la frequencia de las series

Figure~\ref{fig:hists} shows the number $r$ of cointegration vectors given by
the Johansen method for different values of the parameters $L$ and $p$, using
four currencies data, i.e., $l=4$, and 1000 considering iterations ($it=1000$).
\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/histCointVectors}
  \caption{Histogram of the number of cointegration vectors using $p=1$. Four
  possible values for $L$ are shown (100, 1900, 6100 and 10700).
  In the cases of $L=100$ and $L=6100$, most of the time there is little
  cointegration (0 or 4 cointegration vectors). However, for $L=1900$ and
  $L=10700$ significant cointegration is found.}
  \label{fig:hists}
\end{figure}
We know that when there is no cointegration vectors, i.e $r=0$, 
there is no cointegration. In the same way, when $r=l$ reveals that no process is I(1) but,
instead, they are all stationary.
The interesting cases of cointegration are those, where $r$ lies strictly
between $0$ and $l$, i.e. $0<r<l$,

@@

The same experiments, using now $p=5$, were carried out in order to see the
effect on the number of cointegration vectors found. 
Figure~\ref{fig:histsp5} shows that, despite the change in the distribution
of the number of cointegration vectors, the sum of their number with $0<r<4$,
remain nearly the same. 
Therefore we can say that the number of lags doesn't significantly affect
the extent of cointegration found.

>>>>

Figure~\ref{fig:hists} shows the number $r$ of cointegration vectors given by
the Johansen method for different values of the parameters $L$ leaving $p$ set
as $1$, using four currencies data, i.e., $l=4$, and 1000 considering iterations
($it=1000$).
\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/histCointVectors}
  \caption{Histogram of the number of cointegration vectors using $p=1$. Four
  possible values for $L$ are shown (100, 1900, 6100 and 10700).
  In the cases of $L=100$ and $L=6100$, most of the time there is little
  cointegration (0 or 4 cointegration vectors). However, for $L=1900$ and
  $L=10700$ significant cointegration is found.}
  \label{fig:hists}
\end{figure}
We know that when no cointegration vectors can be found, i.e $r=0$, implies that
the variables are not cointegrated. In the same way, when $r=l$ reveals that
none of the processes is I(1) but, they are all stationary.  The interesting cases of
cointegration are those, where $r$ lies strictly between $0$ and $l$, i.e.
$0<r<l$,

@@

The same experiments, setting $p=5$, were carried out in order to see the
effect on the number of cointegration vectors found. 
Figure~\ref{fig:histsp5} shows that, despite the change in the distribution
of the number of cointegration vectors, the sum of the cases where $0<r<4$,
remains nearly the same. 
Therefore, we can say that the number of lags doesn't significantly affect
the extent of cointegration found.
